%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Digital Design IC engineer} % Job title
    {KandouBus Switzerland} % Organization
    {Lausanne, Switzerland} % Location
    {May. 2018 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Digital design}
        \begin{itemize}
          \item {\textbf{Top chip lead role in PCIe SoC (1GHz, 25M gates + memories, 22mm2)}}
          \begin{itemize}
            % How many clocks in the system, number of gates, die area
            \item {Collaboration with cross-functional teams, including architect, hardware, software, and PD teams to ensure that the project's deliverables met the necessary specifications.}
            \item {Experience on designing and implementing LTSSM equalization techniques for PCIe Gen5.}
            \item {Collaborated closely with the IC architecture team, offering expert insights and suggestions to improve their proposed specifications, ultimately resulting in the successful implementation of the project's goals.}
            \item {Conducted thorough review of the verification plan, identified and addressed missing critical checkers, which greatly improved the overall quality and completeness of the verification effort.}
          \end{itemize}
          \item {\textbf{Lead role on CPU system implementation}}
          \begin{itemize}
            % Simulated complete bootload sequence
            \item {Successfully configured and integrated third-party IPs (I2C, SMB, SPI, ...) into the design, meeting project requirements and resulting in a timely delivery of the project's deliverables.}
            \item {Setup and configured the C toolchain in the simulation environment, enabling efficient and accurate testing and validation of designs.}
            \item {Effectively interfaced with external Design Verification (DV) contractors to ensure seamless integration of their deliverables into the project, resulting in successful project completion.}
          \end{itemize}
          \item {\textbf{Implementation of high speed USB SERDES RX blocks (833MHz)}}
          \begin{itemize}
            \item {BIST, Eyescope and various calibration blocks (CTLE, equalizers, ...)}
            \item {Implemented CDC scheme block and validated them with CDC formal app.}
            \item {Logic timing optimizations using timing report feedback.}
            % \item {Designed for testability using ad-hoc logic.}
            \item {Linting analysis with formal app.}
            \item {Wrote detailed documentation of the implemented blocks for the verification and AE team.}
            \item {Developed high level analog model of the whole RX analog chain in SystemVerilog.}
            \item {\textbf{Dynamic power analysis and manual data/clock gating insertion}.}
            % \item {Dicussion for optimizing algorithms from the System team.}
          \end{itemize}
          \item {\textbf{Work flow improvement}}
          \begin{itemize}
            \item {Developed Jenkins CI flow from scratch, which greatly improved the quality of the RTL releases.}
            \item {\textbf{Delivered SVA training for the designers inside the company}.}
            \item {Continuous improvement of the digital development flow (checkers, automation, reconfigurability).}
            \item {Implemented and enforced a Git message policy to ensure clear and consistent communication within the project's code repository.}
          \end{itemize}
        \end{itemize}
        \item {Silicon validation}
          \begin{itemize}
            \item {\textbf{Development of Python scripts and programs for integrated circuit validation, characterization and ATE.}}
            \item {Delivered bring-up and characterization results through Jupyter notebooks}
            \item {Extensive use of python libs (pandas, numpy, matplotlib).}
          \end{itemize}
        % \item {Functional verification}
        % \begin{itemize}
        %   \item {Verification of the SERDES design.}
        %   \item {Drove coverage analysis and reviewed list of waivers with the design/management team.}
        %   \item {Optimization of the verification working flow.}
        %   \begin{itemize}
        %     \item {Setup verification scripting environment based on Python.}
        %     \item {Development of company UVM base classes and UVCs.}
        %       \begin{itemize}
        %         \item {Clock and reset agents.}
        %         \item {Agent and environment base classes.}
        %       \end{itemize}
        %     \item {Development of company assertion libraries.}
        %     \item {\textbf{Defined UVM/SVA verification methodology / coding guidelines for the company}.}
        %   \end{itemize}
        % \end{itemize}
        % \item {Physical design}
        % \begin{itemize}
        %   \item {Responsible of \textbf{Synthesis and Place and Route flow for a digital SERDES IP in 16nm (781.25MHz)}.}
        %   % 500Gbps GW IP, CNRZ 5b6w 6.25 x 4 = 25 Gbps per wire. Per chord -> 125 Gbps. 4 chords -> 500 Gbps
        %   % 1UI clk: 25Ghz
        %   % 32UI clk: 781.25 Mhz
        %   \begin{itemize}
        %     \item {SDC Timing constraints development and validation.}
        %     \item {Signoff checks:}
        %     \begin{itemize}
        %       \item {EMIR and power analysis with Voltus.}
        %       \item {DRC verification.}
        %       \item {Static Timing Analysis and block-level timing closure with Tempus.}
        %       \item {Mixed signal STA between analog and digital datapath.}
        %     \end{itemize}
        %   \end{itemize}
        % \end{itemize}
      \end{cvitems}
      % \begin{cvsubentries}
      %   \cvsubentry{}{Title}{2013}{Description}
      %   % \cvsubentry{}{Smart TV Penetration Testing}{}{}
      %   % \begin{cvitems} % Description(s) of tasks/responsibilities
      %   %   \item {Architecture design, documentation and implementation of LDPC input/output controllers.}
      %   % \end{cvitems}
      % \end{cvsubentries}
    }

  \cventry
    {Digital Verification IC engineer} % Job title
    {} % Organization
    {} % Location
    {May. 2017 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % \item {Silicon validation}
        %   \begin{itemize}
        %     \item {\textbf{Development of Python scripts and programs for integrated circuit validation, characterization and ATE.}}
        %     \item {Delivered bring-up and characterization results through Jupyter notebooks}
        %     \item {Extensive use of python libs (pandas, numpy, matplotlib).}
        %   \end{itemize}
        \item {Functional verification}
        \begin{itemize}
          \item {Verification of the SERDES design.}
          \item {Drove coverage analysis and reviewed list of waivers with the design/management team.}
          \item {Optimization of the verification working flow.}
          \begin{itemize}
            \item {Setup verification scripting environment based on Python.}
            \item {Development of company UVM base classes and UVCs.}
              \begin{itemize}
                \item {Clock and reset agents.}
                \item {Agent and environment base classes.}
              \end{itemize}
            \item {Development of company assertion libraries.}
            \item {\textbf{Defined UVM/SVA verification methodology / coding guidelines for the company}.}
          \end{itemize}
        \end{itemize}
        \item {Physical design}
        \begin{itemize}
          \item {Responsible of \textbf{Synthesis and Place and Route flow for a digital SERDES IP in 16nm (781.25MHz)}.}
          % 500Gbps GW IP, CNRZ 5b6w 6.25 x 4 = 25 Gbps per wire. Per chord -> 125 Gbps. 4 chords -> 500 Gbps
          % 1UI clk: 25Ghz
          % 32UI clk: 781.25 Mhz
          \begin{itemize}
            \item {SDC Timing constraints development and validation.}
            \item {Signoff checks:}
            \begin{itemize}
              \item {EMIR and power analysis with Voltus.}
              \item {DRC verification.}
              \item {Static Timing Analysis and block-level timing closure with Tempus.}
              \item {Mixed signal STA between analog and digital datapath.}
            \end{itemize}
          \end{itemize}
        \end{itemize}
      \end{cvitems}
    }

  % \cventrydouble
  %   {Consultant} % Job title
  %   {Aquantia Corp.} % Organization
  %   {Aachen (D)} % Location
  %   {Aug. 2017 - Present} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Development of a layer 2 Ethernet switch in SystemC. The goal was to create a transmission line model to verify functionality, which could be easily translated into synthesizable code later, using a high-level synthesis suite.}
  %       \item {Support and further development of the FPGA user interface and the power analysis environment which was developed during the internship.}
  %     \end{cvitems}
  %   }
  %   {Intern} % Job title
  %   {San José (USA)} % Location
  %   {Nov. 2016 - July. 2017} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Creation of an automated power analysis environment, build on top of Ansys' PowerArtist. Subsequently, power analysis and reduction on various digital designs was done.}
  %       \item {Development of an intuitive graphical user interface, written in Python, Tkinter, and C, to access and manipulate an FPGA Ethernet debug tool.}
  %     \end{cvitems}
  %   }

% \begin{cvsubentries}
% \end{cvsubentries}

  % \cvsubentry
  %   {Toto}
  %   {Toto}
  %   {Toto}
  %   {Toto}
%---------------------------------------------------------
  \cventry
    {Senior Digital IC engineer} % Job title
    {Marvell Switzerland.} % Organization
    {Etoy, Switzerland} % Location
    {Sep. 2011 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Functional verification.}
        \begin{itemize}
          \item {Assertion Based Verification.}
          \begin{itemize}
            \item {Formal model checking of MAC and control based blocks.}
            \item {\textbf{Assertions profiling with simulators. Optimization of assertions for Simulation/Formal model checking}.}
          \end{itemize}
          \item {UVM methodology.}
          \begin{itemize}
            \item {Constrained Random verification of MAC/PHY blocks.}
            \item {Development of agents, drivers, monitors, scoreboards, observers, sequencers.}
            \item {Developed RAL mechanism into the UVM testbench.}
            \item {Developed full verification environment for LDPC importing System DPI C.}
          \end{itemize}
          \item {Static verification.}
          \begin{itemize}
            \item {\textbf{Strong experience in formal apps: connectivity, register check, assertion generation}}
            \item {Clock domain crossing / Reset verification with 0in cdc}
          \end{itemize}
          \item {Coverage analysis.}
          \begin{itemize}
            \item {Structural coverage (line/expression/condition/toggle/fsm)}
            \item {Functional coverage: defined and implemented covergroups from verification plan}
          \end{itemize}
          \item {Verification Planning.}
          \begin{itemize}
            \item {\textbf{Verification Lead role on FM project}.}
            \item {\textbf{Discussion with design and system team for defining the top verification plan}.}
          \end{itemize}
        \end{itemize}
        \item {Digital design.}
        \begin{itemize}
          \item {Architecture design, documentation and implementation of LDPC input/output controllers.}
          \item {Set up FPGA scripts for plotting LDPC BER/SNR graph}
          \item {\textbf{Optimized memory architecture of front end LDPC} for throughput optimization.}
          \item {DFT LBIST architecture review and designed test control block.}
        \end{itemize}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Master final internship} % Job title
    {Marvell Switzerland.} % Organization
    {Etoy, Switzerland} % Location
    {Feb. 2011 - Sep. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Formal model checking of MAC controller.}
        \item {Developed verification plans from specification.}
        \item {Implemented assertions, constraints from verification plan (SVA).}
        \item {Performed formal model checking.}
      \end{cvitems}
      % \begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      % \end{cvsubentries}
      % \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
    }

  % \begin{cvsubentries}
  %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
  %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
  % \end{cvsubentries}
%---------------------------------------------------------
\end{cventries}
